Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
anonymise
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52746 72bbbca6-d526-0410-a7d9-f06f51895060

\author{Akshay Minocha \\
  IIIT Hyderabad  \\
  Hyderabad (India) \\
  {\small {\tt akshay.minocha@students.iiit.ac.in}} \\\And
  Francis M. Tyers \\
  Giellatekno / CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\small {\tt francis.tyers@uit.no}} \\}

@@

\section{Methodology}
\label{sec:method}
We use the character n-gram approach along with some heuristics which are relevant to our problem domain of identifying
segments for subsequent processing. We would like 
to both predict the code switched points but looking at the surrounding structure also decide the inclusion of them 
into the current or the next segment. \\

@@

We thank Kevin Scannell for help with providing data from Twitter and for useful comments and suggestions.

>>>>

\author{}
%\author{Akshay Minocha \\
%  IIIT Hyderabad  \\
%  Hyderabad (India) \\
%  {\small {\tt akshay.minocha@students.iiit.ac.in}} \\\And
%  Francis M. Tyers \\
%  Giellatekno / CLEAR \\
%  UiT Norgga \'arktala\v{s} universitehta  \\
%  9017 Romsa (Norway) \\
%  {\small {\tt francis.tyers@uit.no}} \\}

@@

\section{Methodology}
\label{sec:method}
We use the character n-gram approach along with some heuristics which are relevant to our problem domain of identifying
segments for subsequent processing. We would like 
to both predict the code switched points but looking at the surrounding structure also decide the inclusion of them 
into the current or the next segment.\footnote{The software used in this experiment is available online at: \url{removed for review}.}

@@

%We thank Kevin Scannell for help with providing data from Twitter and for useful comments and suggestions.
